### 2022-11-01 manuscript.Rmd
Move R references to references
Replace OSF link with DOI

bibliography      : ["manuscript_files/references.bib", "manuscript_files/r-references.bib"]
csl               : "manuscript_files/citation_style.csl"

@@

The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly available.
The code for data analysis is available at [https://osf.io/uksbc/](https://osf.io/uksbc/).

>>>>

bibliography      : "manuscript_files/references.bib"
csl               : "manuscript_files/citation_style.csl"

@@

The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly available.
The code for data analysis is available at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc).
